%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection[page1sidebar]{Recent Work Experience}


\cvevent{\textbf{Fullstack Developer}}{\textbf{1health}}{Feb 2021 - Now}{San Francisco - United States}
\begin{itemize}
    \item Implement upgrading golang project and implement go modules.
    \item Implement TDD for testing functions.
    \item Implement middleware for APIs security.
    \item Implement new features for Python with flask and django.
    \item Implement new task for python with Celery and RabbitMQ.
    \item Worked on issues for React Project.
\end{itemize}

\divider

\cvevent{\textbf{Backend Developer}}{\textbf{Equip Industry}}{Jun 2020 - January 2021}{Lima - Peru}
\begin{itemize}
    \item Implementation Golang project with GraphQL.
    \item Implementation Golang wrapper project for payment gateway(niubiz).
    \item Management Postgres with ent ORM and queries for migrations in Golang.
    \item Management AWS Infrastructure with terraform.
    \item Management servers EC2.
    \item Implement infrastructure for WooCommerce.
    \item Implement functional testing.
\end{itemize}

\divider

\cvevent{\textbf{Backend Developer}}{\textbf{WiserSKILLS}}{February 2020 - May 2020}{Neuilly-sur-Seine - France}
\begin{itemize}
    \item Management Golang project with framework GOA Design.
    \item Management Golang project with gRPC.
    \item Management No-SQL ArangoDB.
    \item Implement plugins for GOA Design.
    \item Implement personalized package to save logs in queues.
    \item Implement functional test for api rest.
    \item Implement functional test for gRPC.
\end{itemize}

\divider

\cvevent{\textbf{Backend Developer} \& \textbf{Mobile Developer}}{\textbf{Devstec}}{Jan 2019 - Jul 2019}{Lima - Peru}
\begin{itemize}
    \item Implement apps worked on flutter.
    \item Implement new APIs in PHP.
    \item Worked on PHP Backend.
\end{itemize}

\divider

\cvevent{\textbf{FullStack Developer} \& \textbf{Mobile Developer}}{\textbf{Mynomx}}{October 2019 - May 2020}{California - United States}
\begin{itemize}
    \item Implement new changes in VueJS project.
    \item Implement new projects for POC on JS.
    \item Implement new APIs in PHP.
    \item Management laravel project to implementing new functionalities.
    \item Management MySQL database with Stored Procedures.
    \item Implement migration of APIs from PHP to Golang.
    \item Implement new apis in Golang.
    \item Implement new calculations based on nutrition.
\end{itemize}

\divider

\cvevent{\textbf{FullStack Developer}}{\textbf{Tecacom}}{Jan 2019 - December 2019}{Lima - Peru}
\begin{itemize}
    \item Implement migration android project to framework Ionic 4.
    \item Implement APIs in PHP for mobile app.
    \item Setting up and provisioning EC2 and RDS server for project.
    \item Monitoring logs and issues for project.
    \item Management wordpress project.
    \item Management new implementation of Laravel project.
    \item Management MySQL databases.
\end{itemize}
